An Extensible Approach to Verification of Embedded Systems

### 2014-05-02 tech-project/led_trans.tex
some changes -- references, etc. Starting work on re-rewriting related work

The \texttt{Leds\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to provide a means of accessing the methods and types in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.

Clearly, facilities and other modules highly reliant on instantiated facilities are no doubt going to consume much more memory than the small example detailed here -- as each would (naively) be represented as a struct. To help alleviate some of this memory usage, we make special considerations in the translated code to only create structs for \textit{enhanced} facilities. That is, \textit{unenhanced} facilities (comprising structs with only a single \texttt{core} field) are not created, but rather, dereferenced manually within the source.

The body of the .c file (omitted from Figure \ref{fig:demo} for clarity and space), operates as expected: A C while loop iterates indefinitely, making successive 500ms delayed calls to toggle each LED. Perhaps the last thing worth mentioning is the invoking main method:

\begin{verbatim}
int main() {
    LED_Telos_Demo_create();
    Main();
    LED_Telos_Demo_destroy();
}
\end{verbatim}

%\texttt{new\_Toggling\_Realiz\_for\_Toggling\_Capability\_of\_LED\_Template()}. Similarly, this initialization and allocation step must occur for the Integer, Boolean, and Clock facilities. From this relatively small example of LED toggling from RESOLVE to C,  complex programs will require even more attention to amount of memory used for each concept and facility realization. Curtailing the management of this memory by placing the responsibility on an allocator provides a key motivation for using \texttt{salloc()} and \texttt{sfree()}.

%As seen from above, RESOLVE to C translations can produce verbose output. The code presented to the right introduces pseudocode for a toggling capability of an LED strip to simplify understanding of control flow. Denoting an LED strip as \texttt{L} and the index represented as an integer literal, this example toggles each LED \footnote{in the case of the telos motes, we will consider the LED strip to have an LED\{0, 1, 2\}} successively, separated by a 500ms delay and is repeated indefinitely through a while-loop.

%Within \texttt{Toggle()}, we use the externally realized LED concepts \texttt{Status()} to get the current state of an LED strip, and \texttt{Set()} to set the specified LED at an index to complement. Retrieving the status, as well as setting an LED strip at an index to on or off requires more memory allocation to save these to temporary Boolean and Integer types. In this instance, we note that we need to have the capability of creating and destroying an arbitrary number of times, provides another key motivation for dynamic memory allocation. Determining the minimum memory size needed, becomes increasingly difficult with the while statement. Similarly, other programs may require an implementation of stacks or queues that require a locally unbounded depth.

%Turning to the \texttt{main} function, we first call the appropriate create function to instantiate and allocate all global variables required by the facility. We then make a call to the user supplied \texttt{Main()} operation, which performs the user code. In normal applications the destroy method will be invoked, however here we employ a busy which prevents it from ever being called.

%A wait utility is then called using the \texttt{Std\_Clock\_Fac} facility. This facility uses the externally realized concept to the msp430 \texttt{\_\_delay\_cycles()} command. Internally the MCU is delayed for a given number of cycles.

%\begin{figure}
%\begin{verbatim}
%int Main() {
%  while(TRUE) {
%    Toggle(L, 0);
%    Wait_500_Milli_Seconds();
%    Toggle(L, 1);
%    Wait_500_Milli_Seconds();
%    Toggle(L, 2);
%    Wait_500_Milli_Seconds();
%  }
%}

%int main() {
%  LED_Telos_Demo_create();
%  Main();
%  LED_Telos_Demo_destroy();
%}
%\end{verbatim}
%\label{fig:loop}
%\end{figure}

>>>>

The \texttt{Leds\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to access the methods and types found in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.

Clearly, facilities and other modules highly reliant on instantiated facilities are no doubt going to consume much more memory than the small example detailed here -- as each would (naively) be represented as a struct. To help alleviate some of this memory usage, we make special considerations in the translator to only create structs for \textit{enhanced} facilities. That is, \textit{unenhanced} facilities (comprising structs with only a single \texttt{core} field) are not created, but rather, dereferenced manually within the source via their \texttt{core} field.

The body of the .c file (omitted from Figure \ref{fig:demo} for reasons of clarity and space), operates largely as one would expect: A while loop iterates indefinitely, making successive, 500ms delayed calls to toggle each LED. Since calls to \texttt{Set}, \texttt{Status}, and \texttt{Toggle} involved in some form or another within this loop, we note that the the task of allocating and deallocating memory used by the local variables within these methods falls to our dynamic allocator.

The main method we use to invoke this logic is shown below.

\begin{verbatim}
int main() {
    LED_Telos_Demo_create();
    Main();
    LED_Telos_Demo_destroy();
}
\end{verbatim}As facility modules are the source of all execution in RESOLVE, this is an ideal place to instantiate all required elements using single call to our facility-defined create method. After execution has completed, the destroy method deallocates all globally declared facilities and variables. Note that the call to destroy for each individual type, in turn calls a similar destroy method defined within the realization for that particular type, resulting in a cascade effect of deallocation.
